\section{Definition and First Properties of Schemes}


\subsection{Locally Ringed Space}

    \begin{definition}\label{def:sheaves}
        Let \(X\) be a topological space.
        A \emph{presheaf} of sets (resp. abelian groups, rings, etc.) on \(X\) is a contravariant functor \(\calF : \Open(X) \to \Set\) (resp. \(\Ab\), \(\Ring\), etc.), 
        where \(\Open(X)\) is the category of open subsets of \(X\) with inclusions as morphisms.

        A presheaf \(\calF\) is a \emph{sheaf} if sections can be glued uniquely.
        More precisely, for every open covering \(\{U_i\}_{i \in I}\) of an open set \(U \subset X\) and every family of sections \(s_i \in \calF(U_i)\) such that \(s_i|_{U_i \cap U_j} = s_j|_{U_i \cap U_j}\) for all \(i,j \in I\),
        there exists a unique section \(s \in \calF(U)\) such that \(s|_{U_i} = s_i\) for all \(i \in I\).
    \end{definition}

    \begin{example}\label{eg:sheaf_of_smooth_and_analytic_functions}
        Let \(X\) be a real (resp. complex) manifold.
        The assignment \(U \mapsto C^\infty(U, \bbR)\) (resp. \(U \mapsto \{\text{holomorphic functions on }U\}\)) defines a sheaf of rings on \(X\).
    \end{example}

    \begin{example}\label{eg:presheaf_but_not_sheaf}
        Let \(X\) be a non-connected topological space.
        The assignment 
        \[U \mapsto \{\text{constant functions on }U\}\] 
        defines a presheaf \(\calC\) of rings on \(X\) but not a sheaf.

        For a concrete example, let \(X = (0,1)\cup (2,3)\) with the subspace topology from \(\bbR\).
        Consider the open covering \(\{(0,1), (2,3)\}\) of \(X\).
        The sections \(s_1 = 1 \in \calC((0,1))\) and \(s_2 = 2 \in \calC((2,3))\) agree on the intersection (which is empty), 
        but there is no global section \(s \in \calC(X)\) such that \(s|_{(0,1)} = s_1\) and \(s|_{(2,3)} = s_2\).
    \end{example}

    \begin{definition}\label{def:locally_ringed_space}
        A \emph{locally ringed space} is a pair \((X, \calO_X)\) where \(X\) is a topological space and \(\calO_X\) is a sheaf of rings on \(X\) such that for every \(x \in X\), the stalk \(\calO_{X,x}\) is a local ring.
        
        A \emph{morphism of locally ringed spaces} \(f : (X, \calO_X) \to (Y, \calO_Y)\) consists of a continuous map \(f : X \to Y\) and a morphism of sheaves of rings \(f^\sharp : \calO_Y \to f_*\calO_X\) 
        such that for every \(x \in X\), the induced map on stalks \(f_x^\sharp : \calO_{Y,f(x)} \to \calO_{X,x}\) is a local homomorphism, 
        i.e., it maps the maximal ideal of \(\calO_{Y,f(x)}\) to the maximal ideal of \(\calO_{X,x}\).
    \end{definition}

    \begin{example}\label{eg:non_local_homomorphism_of_local_rings}
        Let \(p\) be a prime number.
        Then the inclusion \(\bbZ_{(p)} \to \bbQ\) is a homomorphism of local rings but not a local homomorphism.
        Here \(\bbZ_{(p)}\) is the localization of \(\bbZ\) at the prime ideal \((p)\).
    \end{example}

    \begin{example}[Glue morphisms]\label{eg:glue_morphisms_of_locally_ringed_spaces}
        Let \(f : (X, \calO_X) \to (Y, \calO_Y)\) be a morphism of locally ringed spaces.
        If \(U \subset X\) and \(V \subset Y\) are open subsets such that \(f(U) \subset V\), then the restriction \(f|_U : (U, \calO_X|_U) \to (V, \calO_Y|_V)\) is a morphism of locally ringed spaces.
        Conversely, if \(\{U_i\}_{i \in I}\) is an open covering of \(X\) and for each \(i \in I\), we have a morphism \(f_i : (U_i, \calO_X|_{U_i}) \to (Y, \calO_Y)\) such that \(f_i|_{U_i \cap U_j} = f_j|_{U_i \cap U_j}\) for all \(i,j \in I\),
        then there exists a unique morphism \(f : (X, \calO_X) \to (Y, \calO_Y)\) such that \(f|_{U_i} = f_i\) for all \(i \in I\).
    \end{example}

    \begin{example}[Glue locally ringed space]\label{eg:glue_open_locally_ringed_subspace}
        We construct a locally ringed space by gluing open subspaces.
        Let \((X_i, \calO_{X_i})\) be locally ringed spaces for \(i \in I\) and \((U_{ij}, \calO_{X_i}|_{U_{ij}})\) be open subspaces for \(i,j \in I\).
        Suppose we have isomorphisms \(\varphi_{ij} : (U_{ij}, \calO_{X_i}|_{U_{ij}}) \to (U_{ji}, \calO_{X_j}|_{U_{ji}})\) such that
        \begin{enumerate}
            \item \(\varphi_{ii} = \id_{X_i}\) for all \(i \in I\);
            \item \(\varphi_{ij}(U_{ij} \cap U_{ik}) = U_{ji} \cap U_{jk}\) for all \(i,j \in I\);
            \item \(\varphi_{jk}\circ \varphi_{ij} = \varphi_{ik}\) on \(U_{ij} \cap U_{ik}\) for all \(i,j,k \in I\).
        \end{enumerate}
        Then there exists a locally ringed space \((X, \calO_X)\) and open immersions \(\psi_i : (X_i, \calO_{X_i}) \to (X, \calO_X)\) uniquely up to isomorphism such that 
        \begin{enumerate}
            \item \(\varphi_i(U_{ij}) = \psi_i(X_i)\cap \psi_j(X_j)\) for all \(i,j \in I\);
            \item the following diagram 
                \[ \begin{tikzcd}
                    (U_{ij}, \calO_{X_i}|_{U_{ij}}) \arrow[d, "\varphi_{ij}"'] \arrow[r, hook] & (X_i, \calO_{X_i}) \arrow[r, hook, "\psi_i"] & (X, \calO_X) \arrow[d, "="] \\
                    (U_{ji}, \calO_{X_j}|_{U_{ji}}) \arrow[r, hook] & (X_j, \calO_{X_j}) \arrow[r, hook, "\psi_j"] & (X, \calO_X)
                \end{tikzcd} \]
                commutes for all \(i,j \in I\);
            \item \(X = \bigcup_{i \in I} \psi_i(X_i)\).
        \end{enumerate}
        Such \((X, \calO_X)\) is called \emph{the locally ringed space obtained by gluing the \((X_i, \calO_{X_i})\) along the \(\varphi_{ij}\)}.
        
        First \(\varphi_{ij}\) induces an equivalence relation \(\sim\) on the disjoint union \(\coprod_{i \in I} X_i\).
        By taking the quotient space, we can glue the underlying topological spaces to get a topological space \(X\).
        The structure sheaf \(\calO_X\) is given by 
        \[ \calO_X(V) := \left\{ (s_i)_{i \in I} \in \prod_{i \in I} \calO_{X_i}(\psi_i^{-1}(V)) \;\middle|\; s_i|_{U_{ij}} = \varphi_{ij}^\sharp(s_j|_{U_{ji}}) \text{ for all } i,j \in I \right\}. \]
        Easy to check that \((X, \calO_X)\) is a locally ringed space and satisfies the required properties.
        If there is another locally ringed space \((X', \calO_{X'})\) with \(\psi'_i\) satisfying the same properties, then by gluing \(\psi_i' \circ \psi_i^{-1}\) we get an isomorphism \((X, \calO_X) \to (X', \calO_{X'})\).
    \end{example}


\subsection{Schemes}

    % \begin{definition}\label{def:affine_scheme}
    %     Let \(R\) be a ring.
    %     The \emph{spectrum} of \(R\), denoted by \(\Spec R\), is the set of all prime ideals of \(R\) equipped with the Zariski topology, 
    %     where the closed sets are of the form \(V(I) = \{\frakp \in \Spec R : I \subset \frakp\}\) for some ideal \(I \subset R\).
    %     The structure sheaf \(\calO_{\Spec R}\) is defined by
    %     \[ \calO_{\Spec R}(D(f)) = R[1/f], \]
    %     where \(D(f) = \{\frakp \in \Spec R : f \notin \frakp\}\) and \(R_f\) is the localization of \(R\) at the multiplicative set \(\{1, f, f^2, \ldots\}\).
    %     Then \((\Spec R, \calO_{\Spec R})\) is a locally ringed space called an \emph{affine scheme}.
    % \end{definition}

    Let \(R\) be a ring.
    Recall that the \emph{spectrum} of \(R\), denoted by \(\Spec R\), is the set of all prime ideals of \(R\) equipped with the Zariski topology, 
    where the closed sets are of the form \(V(I) = \{\frakp \in \Spec R : I \subset \frakp\}\) for some ideal \(I \subset R\).

    For each \(f \in R\), let \(D(f) = \{\frakp \in \Spec R : f \notin \frakp\}\).
    Such \(D(f)\) is open in \(\Spec R\) and called a \emph{principal open set}.
    
    \begin{proposition}\label{prop:principal_open_sets_form_a_basis}
        Let \(R\) be a ring.
        The collection of principal open sets \(\{D(f) : f \in R\}\) forms a basis for the Zariski topology on \(\Spec R\).
    \end{proposition}
    \begin{proof}
        \Yang{To be continued}
    \end{proof}

    Define a sheaf of rings on \(\Spec R\) by 
    \[ \calO_{\Spec R}(D(f)) = R[1/f]. \]
    Then \((\Spec R, \calO_{\Spec R})\) is a locally ringed space.

    \begin{definition}\label{def:affine_scheme_and_scheme}
        An \emph{affine scheme} is a locally ringed space isomorphic to \((\Spec R, \calO_{\Spec R})\) for some ring \(R\).
        A \emph{scheme} is a locally ringed space \((X, \calO_X)\) which admits an open cover \(\{U_i\}_{i \in I}\) such that \((U_i, \calO_X|_{U_i})\) is an affine scheme for each \(i \in I\).

        A \emph{morphism of schemes} is a morphism of locally ringed spaces.

        These data form a category, denoted by \(\Sch\).
        If we fix a base scheme \(S\), then an \emph{\(S\)-scheme} is a scheme \(X\) together with a morphism \(X \to S\).
        The category of \(S\)-schemes is denoted by \(\Sch/S\) or \(\Sch_S\).
    \end{definition}

    \begin{theorem}\label{thm:equivalence_between_rings_and_affine_schemes}
        The functor \(\Spec : \Ring^{\op} \to \Sch\) is fully faithful and induces an equivalence of categories between the category of rings and the category of affine schemes.
        \Yang{To be continued}
    \end{theorem}

    \begin{definition}\label{def:open_and_closed_immersion}
        A morphism of schemes \(f : X \to Y\) is an \emph{open immersion} (resp. \emph{closed immersion}) if \(f\) induces an isomorphism of \(X\) onto an open (resp. closed) subscheme of \(Y\).
        An \emph{immersion} is a morphism which factors as a closed immersion followed by an open immersion.
        \Yang{To be continued}
    \end{definition}

    \begin{definition}\label{def:scheme_theoretic_image}
        Let \(f : X \to Y\) be a morphism of schemes.
        The \emph{scheme theoretic image} of \(f\) is the smallest closed subscheme \(Z\) of \(Y\) such that \(f\) factors through \(Z\).
        More precisely, if \(Y = \Spec A\) is affine, then the scheme theoretic image of \(f\) is \(\Spec(A/\ker(f^\sharp))\), where \(f^\sharp : A \to \Gamma(X, \calO_X)\) is the induced map on global sections.
        In general, we can cover \(Y\) by affine open subsets and glue the scheme theoretic images on each affine open subset to get the scheme theoretic image of \(f\).
        \Yang{To be continued}
    \end{definition}


    \begin{example}[Glue open subschemes]\label{eg:glue_open_subschemes}
        The construction in \cref{eg:glue_open_locally_ringed_subspace} allows us to glue open subschemes to get a scheme.
        More precisely, let \((X_i, \calO_{X_i})\) be schemes for \(i \in I\) and \((U_{ij}, \calO_{X_i}|_{U_{ij}})\) be open subschemes for \(i,j \in I\).
        Suppose we have isomorphisms \(\varphi_{ij} : (U_{ij}, \calO_{X_i}|_{U_{ij}}) \to (U_{ji}, \calO_{X_j}|_{U_{ji}})\) satisfying the cocycle condition as in \cref{eg:glue_open_locally_ringed_subspace}.
        Then the locally ringed space \((X, \calO_X)\) obtained by gluing the \((X_i, \calO_{X_i})\) along the \(\varphi_{ij}\) is a scheme.
    \end{example}

\subsection{Integral, reduced and irreducible}

\subsection{Fiber product}

\subsection{Dimension}

\subsection{Noetherian and finite type}

\subsection{Separated and proper}
