\section{Birational geometry on surfaces}

Let \(\kkk\) be an algebraically closed field of arbitrary characteristic.
Unless otherwise specified, all varieties are defined over \(\kkk\).


\subsection{Birational map}

    \begin{theorem}
        Let \(X\) and \(Y\) be two smooth projective surfaces over an algebraically closed field \(\kkk\).
        Then any birational map \(f:X\dashrightarrow Y\) can be decomposed as a finite sequence of blow-ups and blow-downs.
        \Yang{To be checked.}
    \end{theorem}

\subsection{Castelnuovo's Theorem and Run the MMP}

    \begin{theorem}[Castelnuovo's contractibility criterion]\label{thm:castelnuovo_contractibility_criterion}
        Let \(X\) be a smooth projective surface over an algebraically closed field \(\kkk\).
        Let \(C\subseteq X\) be an irreducible curve.
        Then there exists a birational morphism \(f:X\to Y\) contracting \(C\) to a smooth point if and only if \(C\cong \bbP^1\) and \(C^2=-1\).
    \end{theorem}

    \begin{definition}\label{def:minimal_surface}
        A \emph{minimal surface} is a smooth projective surface that does not contain any \((-1)\)-curves.
        \Yang{To be checked.}
    \end{definition}

\subsection{Resolution of singularities on surface}

    \begin{theorem}[Resolution of singularities on surfaces]\label{thm:resolution_of_singularities_on_surfaces}
        Let \(X\) be a projective surface over an algebraically closed field \(\kkk\).
        Then there exists a smooth projective surface \(\widetilde{X}\) and a birational morphism \(\pi:\widetilde{X}\to X\) such that \(\pi\) is an isomorphism over the smooth locus of \(X\).
        Moreover, \(\widetilde{X}\) can be obtained from \(X\) by a finite sequence of blow-ups at singular points.
        \Yang{To be checked.}
    \end{theorem}