\section{Kodaira Vanishing Theorem}

\subsection{Preliminary}

    % \begin{theorem}[GAGA]\label{thm: GAGA for cohomology}
    %     Let $X$ be a smooth projective variety over $\mathbb{C}$ and \(\calF\) a coherent sheaf on \(X\).
    %     Then 
    %     \[
    %         H^i(X, \calF) \cong H^i(X^{an}, \calF^{an}).
    %     \]
    % \end{theorem}

    \begin{theorem}[Serre Duality]\label{thm: Serre duality for line bundles}
        Let \(X\) be a Cohen-Macaulay projective variety of dimension \(n\) over \(\kk\) and \(D\) a divisor on \(X\).
        Then there is an isomorphism
        \[
            H^i(X, D) \cong H^{n-i}(X, K_X - D)^\vee, \quad \forall i = 0, 1, \ldots, n.
        \]
    \end{theorem}

    % \begin{theorem}[Serre Vanishing]\label{thm: Serre vanishing theorem}
    %     Let \(X\) be a proper variety of dimension \(n\) over \(\kk\), \(\calF\) a coherent sheaf and \(\calL\) an ample line bundle on \(X\). 
    %     Then there exists an integer \(m_0 > 0\) such that for all \(m \geq m_0\),
    %     \[
    %         H^i(X, L^m\ten \calF) = 0,\quad \forall i > 0.
    %     \]
    % \end{theorem}

    \begin{theorem}[Log Resolution of Singularities]\label{thm: log resolution of singularities}
        Let X be an irreducible reduced algebraic variety over $\bbC$ (or a suitably small neighborhood of a compact set of an irreducible reduced analytic space) and $I \subset \calO_X$ a coherent sheaf of ideals defining a closed subscheme (or subspace) $Z$. Then there is a smooth variety (or analytic space) $Y$ and a projective morphism $f: Y \to X$ such that
        \begin{enumerate}
            \item $f$ is an isomorphism over $X - (\Sing(X) \cup \Supp Z)$,
            \item $f^*I \subset \calO_Y$ is an invertible sheaf $\calO_Y(-D)$ and 
            \item $\Exc(f) \cup D$ is an snc divisor.
        \end{enumerate}
    \end{theorem}

    \begin{theorem}[Lefschetz Hyperplane Theorem]\label{thm: Lefschetz hyperplane theorem}
        Let \(X\) be a smooth projective variety of dimension \(n\) over \(\bbC\) and \(Y\) a hyperplane section of \(X\).
        Then the restriction map
        \[
            H^k(X,\bbC) \to H^k(Y, \bbC)
        \]
        is an isomorphism for \(k < n - 1\) and an injection for \(k = n - 1\).
    \end{theorem}

    \begin{theorem}[Hodge Decomposition]\label{thm: Hodge decomposition}
        Let \(X\) be a smooth projective variety of dimension \(n\) over \(\bbC\).
        Then for any \(k\), there is a functorial decomposition
        \[
            H^k(X, \bbC) = \bigoplus_{p+q=k} H^{p}(X, \Omega^q_X).
        \]
    \end{theorem}

    Combine Theorem \ref{thm: Lefschetz hyperplane theorem} and Theorem \ref{thm: Hodge decomposition}, we have the following lemma.

    \begin{lemma}\label{lem: Lefschetz hyperplane theorem for cohomology of structure sheaf}
        Let \(X\) be a smooth projective variety of dimension \(n\) over \(\bbC\) and \(Y\) a hyperplane section of \(X\).
        Then the restriction map \(r_k: H^k(X,\bbC) \to H^k(Y, \bbC)\) decomposes as 
        \[
            r_k = \bigoplus_{p+q=k} r_{p,q},\quad r_{p,q}: H^{p}(X, \Omega^q_X) \to H^{p}(Y, \Omega^q_Y).
        \]
        And \(r_{p,q}\) is an isomorphism for \(p + q < n - 1\) and an injection for \(p + q = n - 1\).
        In particular, 
        \[ H^p(X, \calO_X) \to H^p(Y, \calO_Y) \]
        is an isomorphism for \(p < n - 1\) and an injection for \(p = n - 1\).
    \end{lemma}

    \begin{theorem}[Leray spectral sequence]\label{thm: Leray spectral sequence}
        Let \(f: Y \to X\) be a morphism of varieties and \(\calF\) a coherent sheaf on \(Y\).
        Then there is a spectral sequence
        \[
            E_2^{p,q} = H^p(X, R^q f_* \calF) \implies H^{p+q}(Y, \calF).
        \]
    \end{theorem}
        

\subsection{Kodaira Vanishing Theorem}

    \begin{lemma}\label{lem: cyclic covering map in Kodaira Vanishing}
        Let \(X\) be a smooth projective variety over \(\kk\) and \(\calL\) a line bundle on \(X\).
        Suppose there is an integer \(m\) and a smooth divisor \(D \in H^0(X, \calL^m)\).
        Then there exists a finite surjective morphism \(f:Y \to X\) of smooth projective varieties such that \(D':= f^{-1}(D)\) is smooth and satisfies that \(bD' = af^*D\).
    \end{lemma}
    \begin{proof}
        Let \(s \in \calL^m\) be the section defining \(D\).
        It induces a homomorphism \(\calL^{-m} \to \calO_X\).
        Consider the \(\calO_X\)-algebra 
        \[ \calA := \left(\bigoplus_{i = 0}^{\infty} \calL^{-i}\right) \bigg/\left(\calL^{-m} \to \calO_X\right) \cong \bigoplus_{i = 0}^{m-1} \calL^{-i}. \]
        Then \(\calA\) is a finite \(\calO_X\)-algebra.
        Let \(Y \coloneqq \Spec_X \calA\).
        Then \(Y\) is a finite \(\calO_X\)-scheme and the natural morphism \(f: Y \to X\) is finite and surjective.

        For every \(x \in X\), let \(\calL\) locally generated by \(t\) near \(x\).
        Then \(\calO_Y\) locally equal to \(\calO_X[t]/(t^m - s)\).
        Let \(D'\) be the divisor locally given by \(t=0\) on \(Y\).
        Since \(X\) and \(D\) are smooth, then \(Y\) is a smooth variety and \(D'\) is smooth.
        Since \(f\) is finite, it is proper.
        Then \(Y\) is proper and hence \(Y\) is projective.
    \end{proof}
    \begin{remark}\label{rmk: cyclic covering map in Kodaira Vanishing can preverse snc}
        Let \(D_i\) be reduced effective divisors on \(X\) such that \(D + \sum_{i=1}^k D_i\) is snc.
        Set \(D_i' = f^*(D_i)\).
        Then \(D' + \sum_{i=1}^k D_i'\) is snc on \(Y\) by considering the local regular system of parameters.
    \end{remark}

    \begin{lemma}\label{lem: injectivity of cohomology of finite pullback of line bundle}
        Let \(f:Y \to X\) be a finite surjective morphism of projective varieties and \(\calL\) a line bundle on \(X\).
        Suppose that \(X\) is normal.
        Then for any \(i \geq 0\), \(H^i(X,\calL)\) is a direct summand of \(H^i(Y, f^*\calL)\).
    \end{lemma}
    \begin{proof}
        Since \(f\) is finite, we have \(H^i(Y, f^*\calL) \cong H^i(X, f_*\calO_Y \ten \calL)\).
        Since \(X\) are normal, the inclusion \(\calO_X \to f_*\calO_Y\) splits by the trace map \((1/n)\Tr_{Y/X}\).
        Thus we have \(f_*\calO_Y \cong \calO_X \oplus \calF\) and hence 
        \[ H^i(X, f_*\calO_Y \ten \calL) \cong H^i(X, \calL) \oplus H^i(X, \calF \ten \calL). \]
        Then the conclusion follows.
    \end{proof}

    \begin{theorem}[Kodaira Vanishing Theorem]\label{thm: Kodaira Vanishing Theorem}
        Let \(X\) be a smooth projective variety of dimension \(n\) over \(\kk\) of characteristic \(0\) and \(A\) an ample divisor on \(X\). 
        Then
        \[
            H^i(X, \calO_X(-A)) = 0,\quad \forall i < n.
        \]
        Equivalently, we have
        \[
            H^i(X, K_X + A) = 0,\quad \forall i > 0.
        \]
    \end{theorem}
    \begin{proof}
        By Lemma \ref{lem: cyclic covering map in Kodaira Vanishing} and \ref{lem: injectivity of cohomology of finite pullback of line bundle}, after taking a multiple of \(A\), we can assume that \(A\) is effective.
        Then we have an exact sequence
        \[ 0 \to \calO_X(-A) \to \calO_X \to \calO_A \to 0. \]
        Taking the long exact sequence of cohomology, we have
        \[ H^{i-1}(X,\calO_X) \to H^{i-1}(X, \calO_A) \to H^{i}(X, \calO_X(-A)) \to H^{i}(X, \calO_X) \to H^{i}(X, \calO_A). \]
        Then the conclusion follows from Lemma \ref{lem: Lefschetz hyperplane theorem for cohomology of structure sheaf} and Serre duality (Theorem \ref{thm: Serre duality for line bundles}).
    \end{proof}


\subsection{Kawamata-Viehweg Vanishing Theorem}

    We list three versions of Kawamata-Viehweg Vanishing Theorem here.

    \begin{theorem}[Kawamata-Viehweg Vanishing Theorem I]\label{thm: Kawamata-Viehweg Vanishing Theorem for nef and big divisor}
        Let \(X\) be a smooth projective variety of dimension \(n\) over \(\kk\) of characteristic \(0\) and \(D\) a nef and big \(\bbr\)-divisor on \(X\).
        Then 
        \[ H^i(X, K_X + D) = 0,\quad \forall i > 0. \]
    \end{theorem}
    \begin{theorem}[Kawamata-Viehweg Vanishing Theorem II]\label{thm: Kawamata-Viehweg Vanishing Theorem in KM98}
        Let \(X\) be a smooth projective variety of dimension \(n\) over \(\kk\) of characteristic \(0\) and \(D\) a nef and big \(\bbQ\)-divisor on \(X\).
        Suppose that \(\lceil D \rceil - D\) has snc support.
        Then
        \[
            H^i(X, K_X + \lceil D \rceil) = 0,\quad \forall i > 0.
        \]
    \end{theorem}
    \begin{theorem}[Kawamata-Viehweg Vanishing Theorem III]\label{thm: Kawamata-Viehweg Vanishing Theorem for klt pair}
        Let \((X,B)\) be a klt pair over \(\kk\) of characteristic \(0\).
        Let \(D\) be a nef \(\bbQ\)-divisor on \(X\) such that \(D + K_{(X,B)}\) is a Cartier divisor.
        Then
        \[ H^i(X, K_{(X,B)} + D) = 0,\quad \forall i > 0. \]
    \end{theorem}

    If we replace the assumption "nef and big" of \(D\) by "ample" in II and III, we denote them as ``II(ample)'' and ``III(ample)'' respectively.
    Then the proof follows the following line:
    \[ \text{Kodaira Vanishing} \implies \text{II(ample)} \implies \text{III(ample)} \implies \text{I} \implies \text{II} \implies \text{III}. \]
    The proofs leave here and the lemmas used in the proofs are collected in the end of this section.
    
    \begin{proof}[Proof of II (\cref{thm: Kawamata-Viehweg Vanishing Theorem in KM98})]
        Set \(M:= \lceil D \rceil\).
        Let 
        \[ B \coloneqq \sum_{i=1}^k b_i B_i \coloneqq \lceil D \rceil - D = M - A, \quad b_i \in (0,1) \cap \bbQ. \]
        We do not require that \(B_i\) are irreducible but we require that \(B_i\) are smooth.

        We induct on \(k\).
        When \(k = 0\), the conclusion follows from \cref{thm: Kawamata-Viehweg Vanishing Theorem for nef and big divisor}.
        (For the ample case, it follows Kodaira Vanishing Theorem (\cref{thm: Kodaira Vanishing Theorem}.))
        Let \(b_k = a/c\) with lowest terms.
        Then \(a<c\).
        By Lemma \ref{lem: divide a divisor by a finite surjective morphism} and \ref{lem: injectivity of cohomology of finite pullback of line bundle}, we can assume that \((1/c)B_k\) is a Cartier divisor (not necessarily effective).
        Applying Lemma \ref{lem: cyclic covering map in Kodaira Vanishing} on \(B_k\),
        we can find a finite surjective morphism \(f: X' \to X\) such that \(f^*B_k = cB_k', B_i' = f^*B_i\) for \(i < k\) and \(\sum_{i=1}^{k} B_i'\) is an snc divisor on \(X'\).
        Let \(B' = \sum_{i=1}^{k-1}B_i', A' = f^*A\) and \(M' = f^*M\).
        Then \(A'+ B' =  M'-aB_k'\) is Cartier.
        Hence by induction hypothesis, \( H^i(X', -A' - B')\) vanishes for \(i > 0\).
        On the other hand, we have
        \[ \calO_{X'}(-M' + aB_k') \cong \sum_{i=0}^{c-1} f^*\calO_X(-M + (a-i) B_k). \]
        Hence \(H^i(X,\calO_X(-M))\) is a direct summand of \(H^i(X', \calO_{X'}(-M' + aB_k'))\) by Lemma \ref{lem: injectivity of cohomology of finite pullback of line bundle}.
    \end{proof}
    \begin{proof}[Proof of III (\cref{thm: Kawamata-Viehweg Vanishing Theorem for klt pair})]
        Let \(f: \tilde{X} \to X\) be a resolution such that \(\Supp f^*B \cup \Exc f\) is snc.
        We can write
        \[ f^*(K_{(X,B)} + D) + E = K_{(\tilde{X},\tilde{B})} + f^*D, \]
        where \(\tilde{B} \in (0,1)\) has snc support and \(E\) is an effective exceptional divisor.

        By \cref{lem:higher_direct_image_of_exceptional_divisor}, we have 
        \[ H^i(\tilde{X}, K_{(\tilde{X},\tilde{B})} + f^*D) = H^i(X, f_*\calO_Y(f^*(K_{(X,B)}+D)+E)) = H^i(X, K_{(X,B)}+D), \] 
        and the left hand vanishes by \cref{thm: Kawamata-Viehweg Vanishing Theorem in KM98} in either case relative to the assumption of \(D\).
    \end{proof}
    \begin{proof}[Proof of I (\cref{thm: Kawamata-Viehweg Vanishing Theorem for nef and big divisor})]
        By \cref{lem:nef_and_big_approximation_by_ample}, we can choose \(k \gg 0\) such that \((X,1/k B)\) is a klt pair with \(D \sim_\bbQ A + \frac{1}{k}B\) for some ample divisor \(A\).
        Then the theorem comes down to \cref{thm: Kawamata-Viehweg Vanishing Theorem for klt pair}.
    \end{proof}

    \begin{lemma}\label{lem:higher_direct_image_of_exceptional_divisor}
        Let \(f:Y \to X\) be a birational morphism of projective varieties with \(Y\) smooth and \(X\) has only rational singularities.
        Let \(E\) be an effective exceptional divisor on \(Y\) and \(D\) a divisor on \(X\).
        Then we have
        \[ f_*(\calO_Y(f^*D + E)) \cong \calO_X(D), \quad R^if_*(\calO_Y(f^*D + E)) = 0,\quad \forall i > 0. \]
    \end{lemma}
    \begin{proof}
        \Yang{I am unable to proof this lemma.}
    \end{proof}

    \begin{lemma}\label{lem: divide a divisor by a finite surjective morphism}
        Let \(X\) be a projective variety, \(\calL\) a line bundle on \(X\) and \(m \in \bbZ_{\geq 0}\).
        Then there exists a finite surjective morphism \(f: Y \to X\) and a line bundle \(\calL'\) on \(Y\) such that \(f^*\calL \sim \calL'^{m}\).
        If \(X\) is smooth, then we can take \(Y\) to be smooth.
        Moreover, if \(D = \sum D_i\) is an snc divisor on \(X\), then we can take \(f\) such that \(f^*D\) is an snc divisor on \(Y\).
    \end{lemma}
    \begin{proof}
        We can assume that \(\calL\) is very ample by writing it as a difference of two very ample line bundles.
        Consider the fiber product \(Y:= \bbp^N \times_{\bbp^N} X\) as the following diagram
        \[ \xymatrix{
            Y \ar[r]^{\psi} \ar[d]_{f} & \mathbb{P}^N \ar[d]^{g} \\
            X \ar[r]^{\varphi_\calL} & \mathbb{P}^N
        }, \]
        where \(g: [x_0: \ldots: x_N] \mapsto [x_0^m: \ldots: x_N^m]\).
        The morphism \(f\) is finite and surjective since so is \(g\).
        Let \(\calL'\coloneqq \psi^*\calL\).

        For smoothness, we can compose \(g\) with a general automorphism of \(\bbp^N\).
        Then the conclusion follows from \cite[Chapter III, Theorem 10.8]{Har77}.
    \end{proof}

    \begin{lemma}[{ref. \cite[Theorem 5.10, 5.22]{KM98}}]\label{lem: klt pair has rational singularities and is Cohen-Macaulay}
        Let \((X,B)\) be a klt pair over \(\kk\) of characteristic \(0\).
        Then \(X\) has rational singularities and is Cohen-Macaulay.
    \end{lemma}

    \begin{lemma}\label{lem:nef_and_big_approximation_by_ample}
        Let \(X\) be a projective variety of dimension \(n\) and \(D\) a nef and big divisor on \(X\).
        Then there exists an effective divisor \(B\) such that for every \(k\), there is an ample divisor \(A_k\) such that 
        \[ D \sim_\bbQ A_k + \frac{1}{k}B. \]
    \end{lemma}
    \begin{proof}
        By \Yang{definition} of big divisor, there exists an ample divisor \(A_1\) and effective divisor \(B\) such that
        \[ D \sim_\bbQ A_1 + B. \]
        Then we have 
        \[ D \sim_\bbQ \frac{A + (k-1)D}{k} + \frac{1}{k}B. \]
        Since \(A\) is ample and \(D\) is nef, we can take \(A_k = (A + (k-1)D)/k\) which is ample.
        % \Yang{To be completed.}
    \end{proof}
 
    
    % \begin{lemma}\label{lem: vanishing for ample plus snc divisor}
    %     Let \(X\) be a smooth projective variety of dimension \(n\) over \(\kk\) of characteristic \(0\), \(A\) an ample divisor and \(E\) an snc divisor on \(X\).
    %     % Suppose that \(E\) is an effective divisor on \(X\) with snc support.
    %     Then
    %     \[
    %         H^i(X, K_X + A + E) = 0,\quad \forall i > 0.
    %     \]
    % \end{lemma}
    % \begin{proof}
    %     Let \(E = \sum_{i=1}^k E_i\).
    %     We induct on \(k\).
    %     Consider the exact sequence
    %     \[ 0 \to \calO_X(-A-\sum_{i=1}^{k} E_i) \to \calO_X(-A-\sum_{i=1}^{k-1} E_i) \to \calO_{E_k}(-A-\sum_{i=1}^{k-1} E_i) \to 0. \]
    %     \Yang{To be completed.}
    % \end{proof}